STAT 253 Final Project

### 2022-10-13 Final_Project_Work_HW2.Rmd
More for HW3

```{r}
gam_spec <- 
  gen_additive_mod() %>%
  set_engine(engine = 'mgcv') %>%
  set_mode('regression')

@@

```{r}
gam_mod %>% pluck('fit') %>% mgcv::gam.check() 
```

```{r}
gam_mod %>% pluck('fit') %>% plot()
```

```{r}
lm_spec_gam <-
  linear_reg() %>%
  set_engine(engine = 'lm') %>%
  set_mode('regression')

@@

fit_resamples(
    movie_wf,
    resamples = data_cv10, # cv folds
    metrics = metric_set(mae,rmse,rsq)                     
) %>% collect_metrics()
```

>>>>

# Update your models to use natural splines for some of the quantitative predictors to account for non-linearity (these are GAMs).

```{r}
# Build the GAM

gam_spec <- 
  gen_additive_mod() %>%
  set_engine(engine = 'mgcv') %>%
  set_mode('regression')

@@

```{r}
# Diagnostics: Check to see if the number of knots is large enough (if p-value is low, increase number of knots)

gam_mod %>% pluck('fit') %>% mgcv::gam.check() 
```

```{r}
# Visualize: Look at the estimated non-linear functions

gam_mod %>% pluck('fit') %>% plot()
```

```{r}
# Use the edf (round to integer) from above to create a recipe by adding step_ns() for the variables you want model with a non-linear relationship and do CV. Compare this model to one without any splines.

lm_spec_gam <-
  linear_reg() %>%
  set_engine(engine = 'lm') %>%
  set_mode('regression')

# data_cv10 <- imdb_clean %>% 
#     filter(No_of_Votes < 1500000 & IMDB_Rating < 9) %>% # remove outliers
#     vfold_cv(v = 10)

data_cv10 <- vfold_cv(imdb_clean, v = 10)

@@

fit_resamples(
    movie_wf,
    resamples = data_cv10, # cv folds
    metrics = metric_set(mae,rmse,rsq)                     
) %>% collect_metrics()

# This code chunk has an error, but I'm not sure why

# fit_resamples(
#     spline_wf,
#     resamples = data_cv10, # cv folds
#     metrics = metric_set(mae,rmse,rsq)                     
# ) %>% collect_metrics()
```

# Compare insights from variable importance analyses here and the corresponding results from the Investigation

```{r}
# Lasso Model Spec with tune
gam_lasso_spec_tune <- 
  linear_reg() %>%
  set_args(mixture = 1, penalty = tune()) %>% ## mixture = 1 indicates Lasso
  set_engine(engine = 'glmnet') %>% #note we are using a different engine
  set_mode('regression')

# Workflow (Recipe + Model)
lasso_wf_tune <- workflow() %>% 
  add_recipe(data_rec) %>%
  add_model(gam_lasso_spec_tune)

# Compare model performance between your GAM models that the models that assuming linearity.

# Summarize investigations

Decide on an overall best model based on your investigations so far. To do this, make clear your analysis goals. Predictive accuracy? Interpretability? A combination of both?
